### 2019-03-11 manuscript/discussion.tex
- minor change to Discussion, diploidization part
removed some tex warnings

%B: v2.0
Diploidization is widely considered to be relatively rare, compared with polyploidization, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history. %cite
As a consequence, it is possible that nearly all extant species classified as ``diploid" in our analyses, based on cytogenetic data, are possibly secondary diploids, having undergone both polyploidization and re-diploidization.
Unduly ignoring secondary diploidization would clearly underestimate the rate of transitions from polyploids to diploids, and would likely cause inflated net diversification rates for diploids.
We find weak support for inclusion of diploidization. %cite fig and expand (FIXME).

Genomic evidence indicates that a paleo-polyploidization may have occurred prior to the origin of the family Solanaceae, rendering all current `diploids' secondarily derived. 
First, \citet{ku2000} and \citet{blanc2004} posited that the lineage leading to tomato, \textit{Solanum lycopersicum}, may have experienced one or more WGDs.
A subsequent analysis of synteny between grape and \textit{Solanum} genomes, as well as the distribution between inferred paralogs within genomes of \textit{Solanum} (tomato and potato) each suggested that this lineage experienced a likely round of ancient genome duplication or triplication \citep{tomato2012}. 
The age of the peak of paralog Ks distances, is approximately 71 million years \citep{tomato2012}. 
If this is the case, then all of the genomes may have been subsequently re-diploidized, yielding the common extant base chromosome numbers in this and related families, n=11-12, considered diploid \citep{robertson2011}. 
%Not unlikely, because Arabidopsis n=5.

On the other hand, there is little evidence for occurrence of re-diploidization within the nightshades.
First, the Ks-inferred duplication long pre-dates the origin of the family \citep{sarkinen_2013}. 
The best-supported, most-recent WGD, which may represent a reversion from polyploidy to diploidy, is older than the lineage under consideration in this study.
At best, the species we consider are ancestrally diploid, having re-diploidized after a suspected WGD.
Second, studies comparing map-based genome synteny within the family find no evidence for recent diploidization \citep{wu_2010a}.
Instead, simple genome re-arrangements appear sufficient to explain chromosomal evolution between a number of species, including all of those in the relatively cytogenetically conserved `x=12' group, which includes tomato, potato, eggplant, pepper, and tobacco.
%B: Once this is re-arranged, and made to fit with the rest of the discussion, add what this has to do with re-diploidization and how to interpret $\delta$.
It is perhaps not surprising that models diploidization in our study recovered wide credible intervals for the diploidization parameter, $\delta$. 
Despite the limitations of assignment of ploidy levels, we found some support for models that include pararmeter $\delta$, meaning that further study may be warranted, especially in other groups.
%Moreover, rare state changes may not be easily recovered. Emma, you had a clever way to summarize this. 
%     meaning of diploidization parameter

>>>>

%B: v2.0
\subsection*{Diploidization}

Diploidization is widely considered to be relatively rare, compared with polyploidization, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history. %cite
As a consequence, it is possible that nearly all extant species classified as ``diploid" in our analyses, based on cytogenetic data, are possibly secondary diploids, having undergone both polyploidization and re-diploidization.
Unduly ignoring secondary diploidization would clearly underestimate the rate of transitions from polyploids to diploids, and would likely cause inflated net diversification rates for diploids.
We find weak support for inclusion of diploidization. %cite fig and expand (FIXME).

Genomic evidence indicates that a paleo-polyploidization may have occurred prior to the origin of the family Solanaceae, rendering all current `diploids' secondarily derived. 
First, \citet{ku2000} and \citet{blanc2004} posited that the lineage leading to tomato, \textit{Solanum lycopersicum}, may have experienced one or more WGDs.
A subsequent analysis of synteny between grape and \textit{Solanum} genomes, as well as the distribution between inferred paralogs within genomes of \textit{Solanum} (tomato and potato) each suggested that this lineage experienced a likely round of ancient genome duplication or triplication \citep{tomato2012}. 
The age of the peak of paralog Ks distances, is approximately 71 million years \citep{tomato2012}. 
If this is the case, then all of the genomes may have been subsequently re-diploidized, yielding the common extant base chromosome numbers in this and related families, n=11-12, considered diploid \citep{robertson_2011}. 
%Not unlikely, because Arabidopsis n=5.

On the other hand, there is little evidence for occurrence of re-diploidization in the time frame we considered, within the nightshades.
First, the Ks-inferred duplication long pre-dates the origin of the family \citep{sarkinen_2013}. 
The best-supported, most-recent WGD, which may represent a reversion from polyploidy to diploidy, is older than the lineage under consideration in this study.
At best, the species we consider are ancestrally diploid, having re-diploidized after a suspected WGD.
Second, studies comparing map-based genome synteny within the family find no evidence for recent diploidization \citep{wu_2010a}.
Instead, simple genome re-arrangements appear sufficient to explain chromosomal evolution between a number of species, including all of those in the relatively cytogenetically conserved `x=12' group, which includes tomato, potato, eggplant, pepper, and tobacco.
%B: Once this is re-arranged, and made to fit with the rest of the discussion, add what this has to do with re-diploidization and how to interpret $\delta$.
It is perhaps not surprising that models diploidization in our study recovered wide credible intervals for the diploidization parameter, $\delta$. 
Despite the limitations of assignment of ploidy levels, we found some support for models that include pararmeter $\delta$, meaning that further study may be warranted, especially in other groups.
%Moreover, rare state changes may not be easily recovered. Emma, you had a clever way to summarize this. 
%     meaning of diploidization parameter
